---
title: "Discussion Week 1"
output: html_document
---

# Working directory

## Your working directory is the folder on your computer in which you are currently working.

## Show current working directory

```{r}
getwd()
```

## Set working directory before you start working

```{r}
setwd("D:/desktop/ucsd/TA 181A WI23/week1")
```

# Getting Help

## When you know the function

```{r}
help(log)
?log
```

## If you just have a fuzzier idea

```{r}
help.search("log")
??log
```

# Simple Calculation

```{r}
7+10
2*3
2^3
sqrt(9)
```

# Variables

## Use '\<-' or '=' operator to assign a value to a variable

```{r}
x <- 3.1
x = 3.1
x #print x
```

```{r}
(x+2)/3 #do calculation with x
```

```{r}
y <- exp(2*x)-1
y
```

## List all variables in the environment

```{r}
ls()
```

## To remove all variables from R's memory

```{r}
rm(list=ls())
```

# Vectors

## A vector is a sequence of elements of the same basic type.

```{r}
x <- c(5, 10, 50.6)
x
```

```{r}
y <- seq(from=0, to=10, by=0.25) #by: increment of the sequence
y
```

```{r}
z <- seq(from=0, to=0.75, len=10)
z
```

# Vectors: operation

## Vector operations are element-wise

```{r}
(1:5) + 1
```

```{r}
(1:5) + (3:7)
```

```{r}
(1:5)^2
```

```{r}
(1:5) * (3:7)
```

## Matrix multiplication

```{r}
(1:5) %*% (3:7)
```

## We can also apply functions to vectors

```{r}
sum(x)
mean(x)
sd(x)
```

# Vectors: indexing

```{r}
x
x[1]
x[5]
```

```{r}
x[3] <- 10.6
x
```

```{r}
x[1:3]
```

```{r}
x[-2]
x[c(1,3)]
```

# Data types: Matrices

## A matrix has two dimensions

```{r}
mat <- matrix(data=c(9,2,3,4,5,6), ncol=3)
mat
```

```{r}
mat <- matrix(data=c(9,2,3,4,5,6), ncol=3, byrow=TRUE)
mat
```

## Matrix-operation are similar to vector operation.

```{r}
mat[1, 2]
mat[2, ]
mean(mat)
```

```{r}
dim(mat)
```

# Data types: Data frames

## Data frames are matrix-like structures, but columns can be of different types

```{r}
t = data.frame(x = c(11,12,14), y = c(19,20,21), z = c("a","b","c"))
t
```

## Select the column 'x'

```{r}
mean(t$x)
mean(t[["x"]])
mean(t[ ,"x"])
```

# Probability functions

## For most probability distributions, R provides the following functions:

ddist: density pdist: probability qdist: quantile rdist: random samples

```{r}
x <- seq(-5, 5, by=0.1)
d <- dnorm(x); p <- pnorm(x)
par(mfrow = c(1,2))
plot(x, d)
plot(x, p)
```

## Generate random variables

```{r}
x <- rnorm(1000) #generate 1000 standard normally distributed r.v., stored in a vector.
y <- rnorm(1000, mean=50, sd=.1)
par(mfrow = c(1,2))
hist(x, main = NULL)
hist(y, main = NULL)
```

# Control flow: If-statement

```{r}
w = 2
if (w<5){
  d=2
} else {
  d=10
}
d
```

# Control flow: For-loop

```{r}
h = seq(from=1, to=8)
s = c()
for (i in 2:10){
  s[i]= h[i]*10
}
s
```

# Hint for homework 1: R simulation

Generate and plot 1 paths of sample means from $n=1$ to $n=40$ for case (a): $(X_1+...+X_n)/n$.

```{r}
# sampling
n = 40
x = runif(n, 0, 2)

# generate y[i] = (x[1]+...+x[i])/i
y = rep(0, n)
for (i in 1:n){
  y[i] = mean(x[1: i])
}

# plot
plot(1:n, y, type = 'l', ylim = c(0, 2))

x = runif(n, 0, 2)
# generate y[i] = (x[1]+...+x[i])/i
y = rep(0, n)
for (i in 1:n){
  y[i] = mean(x[1: i])
}

for(j in 1:9){
  x = runif(n, 0, 2)
  # generate y[i] = (x[1]+...+x[i])/i
  y = rep(0, n)
  for (i in 1:n){
    y[i] = mean(x[1: i])
  }
  lines(1:n, y)
}

```

Then use function 'lines' to plot the other 9 paths in the same plot. Also, plot 10 paths for case (b) using similar method.



```{r}
# sampling
n = 40
x = runif(n, 0, 2)^2

# generate y[i] = (x[1]+...+x[i])/i
y = rep(0, n)
for (i in 1:n){
  y[i] = mean(x[1: i])
}

# plot
plot(1:n, y, type = 'l', ylim = c(0, 4))

x = runif(n, 0, 2)
# generate y[i] = (x[1]+...+x[i])/i
y = rep(0, n)
for (i in 1:n){
  y[i] = mean(x[1: i])
}

for(j in 1:9){
  x = runif(n, 0, 2)^2
  # generate y[i] = (x[1]+...+x[i])/i
  y = rep(0, n)
  for (i in 1:n){
    y[i] = mean(x[1: i])
  }
  lines(1:n, y)
}

```